Formalization of Network Flow Algorithms

### 2017-03-02 paper/root.tex
fixed code and listing indentations
Fixed the diagrams

\input{lstisabelle}
\lstset{basicstyle=\footnotesize\ttfamily\slshape}
\lstset{captionpos=b}
\lstset{numberbychapter=false}
\lstset{autogobble=true}

@@

% Include snippets
\newcommand{\DefineSnippet}[2]{%
   \expandafter\newcommand\csname snippet--#1\endcsname{%
     \begin{quote}
     \begin{isabelle}\footnotesize
     #2
     \end{isabelle}
     \end{quote}}}
\newcommand{\Snippet}[1]{\ifcsname snippet--#1\endcsname\csname snippet--#1\endcsname\else\PackageError{}{No snippet '#1' defined.}{}\fi}
\input{snippets/snippets.out}

@@

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1k$, $2k$, $3k$, $4k$, $5k$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{dashed, every mark/.append style={solid, fill=gray}, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

		%start data for plotting
		  \addplot+[mark=square] table {
		    1000 .024   
		    1500 .098  
		    2000 .211  
		    2500 .693  
		    3000 2.014 
		    3500 3.153 
		    4000 3.679 
		    4500 8.364 
		    5000 10.328 
		    5500 11.749    
		  }; %Sparse, Edka, SML

		  \addplot+[dashed, every mark/.append style={solid, fill=gray},mark=*] table {
		    1000 .024   
		    1500 .054   
		    2000 .103  
		    2500 .399  
		    3000 .719  
		    3500 1.362 
		    4000 2.036 
		    4500 3.334 
		    5000 4.785 
		    5500 6.079     
		  }; %Sparse, Edka, Java

		  \addplot+[mark=square*] table {
		    1000 .005   
		    1500 .013  
		    2000 .024  
		    2500 .037  
		    3000 .066 
		    3500 .077 
		    4000 .096 
		    4500 .146 
		    5000 .194 
		    5500 .192    
		  }; %Sparse, Prpu, SML 
		%end data for plotting

@@

		%start data for plotting 
		  \addplot+[mark=square] table {
		    1000	2.794
		    1050	2.9
		    1100	4.405
		    1150	4.435
		    1200	5.232
		    1250	6.029
		    1300	7.699
		    1350	8.91
		    1400	7.225
		    1450	10.042 
		  }; %Dense, Edka, SML

		  \addplot+[dashed, every mark/.append style={solid, fill=gray},mark=*] table {
		    1000	3.982
		    1050	4.463
		    1100	5.278
		    1150	6.27
		    1200	6.939
		    1250	7.953
		    1300	9.392
		    1350	10.317
		    1400	14.71
		    1450	13.11  
		  }; %Dense, Edka, Java

		  \addplot+[mark=square*] table {
		    1000	0.074
		    1050	0.059
		    1100	0.068
		    1150	0.075
		    1200	0.102
		    1250	0.085
		    1300	0.096
		    1350	0.103
		    1400	0.088
		    1450	0.114  
		  }; %Dense, Prpu, SML  
		%end data for plotting

@@

    %start data for plotting

		  \addplot+[mark=square] table {
        3000	0.356
        4500	0.805
        6000	1.539
        7500	2.43
        9000	3.28
        10500	4.639
        12000	5.61
        13500	7.198
        15000	8.904
        16500	11.302
		  }; %Wash, Edka, SML

      \addplot+[mark=square*] table {
        3000	1.185
        4500	3.524
        6000	6.457
        7500	11.509
        9000	17.529
        10500	26.185
        12000	36.828
        13500	48.614
        15000	86.449
        16500	89.661
      }; %WASH, Prpu, SML

      \addplot+[mark=o] table {
        3000	0.906
        4500	2.708
        6000	5.083
        7500	8.792
        9000	12.951
        10500	19.075
        12000	27.466
        13500	35.964
        15000	61.839
        16500	67.039
      }; %WASH, Prpu, C++

      \addplot+[mark=otimes*] table {
        3000	0.006
        4500	0.015
        6000	0.029
        7500	0.042
        9000	0.063
        10500	0.084
        12000	0.115
        13500	0.144
        15000	0.183
        16500	0.223
      }; %WASH, Prpu, C

@@

    %start data for plotting 
      \addplot+[mark=square*] table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; %ACNET, Prpu, SML

      \addplot+[mark=o] table {
        1000	0.121
        1050	0.17
        1100	0.123
        1150	0.216
        1200	0.197
        1250	0.237
        1300	0.298
        1350	0.621
        1400	0.399
        1450	0.486
      }; %ACNET, Prpu, C++

      \addplot+[mark=otimes*] table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; %ACNET, Prpu, C

@@

    %start data for plotting
      \addplot+[mark=square*] table {
        16000	3.602
        17600	4.223
        19200	4.839
        20800	8.201
        22400	8.273
        24000	13.426
        25600	10.089
        27200	15.889
        28800	16.431
        30400	21.437
      }; %RPFGEN, Prpu, SML

      \addplot+[mark=o] table {
        16000	4.51
        17600	4.804
        19200	5.899
        20800	8.052
        22400	8.448
        24000	11.555
        25600	8.878
        27200	13.999
        28800	12.99
        30400	13.791
      }; %RPFGEN, Prpu, C++

      \addplot+[mark=otimes*] table {
        16000	0.009
        17600	0.012
        19200	0.015
        20800	0.021
        22400	0.021
        24000	0.019
        25600	0.023
        27200	0.028
        28800	0.026
        30400	0.026
      }; %RPFGEN, Prpu, C  
    \end{groupplot}

>>>>

\input{lstisabelle}
\lstset{basicstyle=\footnotesize\ttfamily\slshape}
\lstset{captionpos=b}
\lstset{numberbychapter=false}
\lstset{autogobble=true}
\lstset{xleftmargin=.15in, xrightmargin=.15in}

%change both above and following margins to have consistent indentation
\newenvironment{lstquote}%
  {\list{}{\leftmargin=0.15in\rightmargin=0.15in}\item[]}%
  {\endlist}

@@

% Include snippets
\newcommand{\DefineSnippet}[2]{%
   \expandafter\newcommand\csname snippet--#1\endcsname{%
     \begin{lstquote} 
     \begin{isabelle}\footnotesize
     #2
     \end{isabelle}
     \end{lstquote}}}
\newcommand{\Snippet}[1]{\ifcsname snippet--#1\endcsname\csname snippet--#1\endcsname\else\PackageError{}{No snippet '#1' defined.}{}\fi}
\input{snippets/snippets.out}

@@

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1k$, $2k$, $3k$, $4k$, $5k$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{fill=gray, mark=*}
      \addlegendimage{mark=square}
      \addlegendimage{every mark/.append style={solid, fill=gray}, mark=o}
      \addlegendimage{dashed, every mark/.append style={solid, fill=gray}, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

		%start data for plotting
		  \addplot+[mark=square*] table {
        1000	0.024
        1500	0.099
        2000	0.211
        2500	1.66
        3000	1.616
        3500	2.966
        4000	3.758
        4500	8.167
        5000	10.222
        5500	12.024
		  }; %Sparse, Edka, SML

		  \addplot+[mark=square] table {
        1000	0.024
        1500	0.05
        2000	0.241
        2500	0.795
        3000	0.689
        3500	1.322
        4000	2.022
        4500	3.345
        5000	4.675
        5500	6.411
		  }; %Sparse, Edka, Java

		  \addplot+[mark=*] table {
        1000	0.005
        1500	0.018
        2000	0.038
        2500	0.07
        3000	0.063
        3500	0.074
        4000	0.098
        4500	0.148
        5000	0.196
        5500	0.191
		  }; %Sparse, Prpu, SML 
		%end data for plotting

@@

		%start data for plotting 
		  \addplot+[mark=square*] table {
        1000	2.777
        1050	2.875
        1100	4.43
        1150	4.466
        1200	5.2
        1250	6.025
        1300	7.654
        1350	9.312
        1400	7.462
        1450	10.279
		  }; %Dense, Edka, SML

		  \addplot+[mark=square] table {
        1000	3.892
        1050	4.773
        1100	5.262
        1150	6.02
        1200	6.974
        1250	7.947
        1300	9.511
        1350	10.754
        1400	11.815
        1450	13.034 
		  }; %Dense, Edka, Java

		  \addplot+[mark=*] table {
        1000	0.058
        1050	0.06
        1100	0.068
        1150	0.075
        1200	0.103
        1250	0.085
        1300	0.097
        1350	0.104
        1400	0.089
        1450	0.114
		  }; %Dense, Prpu, SML  
		%end data for plotting

@@

    %start data for plotting 
		  \addplot+[mark=square*] table {
        3000	0.36
        4500	0.813
        6000	1.565
        7500	2.435
        9000	3.313
        10500	4.69
        12000	5.693
        13500	9.676
        15000	9.284
        16500	11.31
		  }; %Wash, Edka, SML

      \addplot+[mark=*] table {
        3000	1.187
        4500	3.654
        6000	7.491
        7500	11.455
        9000	18.457
        10500	27.253
        12000	38.922
        13500	51.136
        15000	86.261
        16500	84.913
      }; %WASH, Prpu, SML

      \addplot+[every mark/.append style={solid, fill=gray}, mark=o] table {
        3000	0.183
        4500	0.521
        6000	0.974
        7500	1.73
        9000	2.579
        10500	3.819
        12000	5.562
        13500	7.184
        15000	12.398
        16500	12.58
      }; %WASH, Prpu, C++

      \addplot+[dashed, every mark/.append style={solid, fill=gray}, mark=otimes*] table {
        3000	0.008
        4500	0.015
        6000	0.027
        7500	0.043
        9000	0.064
        10500	0.095
        12000	0.124
        13500	0.16
        15000	0.2
        16500	0.259
      }; %WASH, Prpu, C

@@

    %start data for plotting 
      \addplot+[mark=*] table {
        1000	0.353
        1050	0.213
        1100	0.247
        1150	0.301
        1200	0.672
        1250	0.703
        1300	0.273
        1350	0.71
        1400	0.277
        1450	1.141
      }; %ACNET, Prpu, SML

      \addplot+[every mark/.append style={solid, fill=gray}, mark=o] table {
        1000	0.046
        1050	0.031
        1100	0.034
        1150	0.039
        1200	0.073
        1250	0.065
        1300	0.038
        1350	0.071
        1400	0.036
        1450	0.104
      }; %ACNET, Prpu, C++

      \addplot+[dashed, every mark/.append style={solid, fill=gray}, mark=otimes*] table {
        1000	0.092
        1050	0.122
        1100	0.116
        1150	0.143
        1200	0.179
        1250	0.108
        1300	0.202
        1350	0.184
        1400	0.146
        1450	0.179
      }; %ACNET, Prpu, C

@@

    %start data for plotting
      \addplot+[mark=*] table {
        16000	3.334
        17600	4.538
        19200	5.844
        20800	6.391
        22400	8.308
        24000	8.242
        25600	18.534
        27200	12.174
        28800	16.653
        30400	19.968
      }; %RPFGEN, Prpu, SML

      \addplot+[every mark/.append style={solid, fill=gray}, mark=o] table {
        16000	0.775
        17600	0.966
        19200	1.496
        20800	1.29
        22400	1.598
        24000	1.525
        25600	2.145
        27200	2.035
        28800	2.478
        30400	2.745
      }; %RPFGEN, Prpu, C++

      \addplot+[dashed, every mark/.append style={solid, fill=gray}, mark=otimes*] table {
        16000	0.009
        17600	0.011
        19200	0.013
        20800	0.012
        22400	0.017
        24000	0.017
        25600	0.021
        27200	0.024
        28800	0.024
        30400	0.022
      }; %RPFGEN, Prpu, C  
    \end{groupplot}
